%*******************************************************************************************%
%            	DYNAMIC MODELLING AND CONTROL OF BALANCED PARALLEL MECHANISMS           	%
% 																					   		%
% July 11, 2014														 						%
% Authors: Renato M. M. Orsino, Andre G. Coutinho, Tarcisio A. H. Coelho					%
% bash adaptive.sh							 												%
% 																							%
%*******************************************************************************************%



%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,11pt,brazil,fleqn]{article}
\synctex=1
%%%%%%%%%%%%%%%%%%%%%%

% \usepackage{natbib}
\usepackage[english]{babel}
% \usepackage{amsmath,amssymb,amsthm,amsfonts,textcomp}
% \usepackage{eucal,eufrak,mathrsfs,bbm,stmaryrd}
\usepackage{color}
\usepackage{amsthm}
\usepackage{array,hhline,supertabular}
\usepackage[colorlinks,citecolor=black,urlcolor=black,linkcolor=black]{hyperref}
\usepackage[pdftex]{graphicx}
\usepackage{multicol}
\usepackage[symbol]{footmisc}
\usepackage{enumitem}
\usepackage{float}
\usepackage{titlesec}
\usepackage{nomencl}
\usepackage{EXTRAS/special-char}
\usepackage{EXTRAS/special-conf}
\usepackage{subfigure}

\graphicspath{{FIGURES/}{../FIGURES/}}
\makenomenclature


%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%

\noindent
{\bf \huge Dynamic modelling and control of balanced parallel mechanisms}\\

\noindent
{\Large 	Renato Maia Matarazzo Orsino$\,{}^\text{a}$, 
			Andr\'e Garnier Coutinho$\,{}^\text{b}$,
			Tarcisio Antonio Hess Coelho$\,{}^\text{c}$
}\\

\noindent
{${}^\text{a}$ \it Department of Mechanical Engineering, Escola Politecnica, University of Sao Paulo, Brazil.
E-mail: renato.orsino@gmail.com}

\noindent
{${}^\text{b}$ \it Department of Mechatronics and Mechanical Systems Engineering, Escola Politecnica, 
University of Sao Paulo, Brazil. E-mail: andre.garnier.coutinho@usp.br}

\noindent
{${}^\text{c}$ \it Department of Mechatronics and Mechanical Systems Engineering, Escola Politecnica, 
University of Sao Paulo, Brazil. E-mail: tarchess@usp.br}

\vspace{24pt}

% \begin{multicols}{1}

\begin{abstract}
Balancing is an important issue related to the design of mechanical systems in general,
and also parallel mechanisms, in particular. In fact, the performance of parallel mechanisms
associated to specific applications depends on the choice of the balancing method, namely, 
either static or dynamic, either passive or active, whether it is valid for a given trajectory
or even for any motion.
The main contribution of this work is to highlight the importance of the dynamic modelling 
process in order to achieve the compensation conditions associated to the chosen 
balancing technique. Due to the fact that parallel mechanisms have highly complex structures,
the use of dynamic formalisms that employ redundant generalized coordinates,
in association with the successive coupling of additional balancing elements 
to the original system model, can bring remarkable benefits.
Additionally, this book chapter also discusses the impact of
the dynamic model, developed in accordance with the methodology shown here, for the 
control strategy of parallel mechanisms.
Finally, the simulation results demonstrates
how effective is the presented methodology for the planar 5-bar with revolute joints (5R). 

\vspace{10pt}

\noindent
KEYWORDS: {Dynamic modelling, balancing, parallel mechanisms, control}
\end{abstract}



\input{EXTRAS/symbols}


%--------------------INTRODUCTION--------------------%

\input{SECTIONS/TARCISIO/1}


%--------------------MODELING--------------------%

\input{SECTIONS/RENATO/2-1}

\input{SECTIONS/RENATO/2-2}

\input{SECTIONS/ANDRE/2-3}

\input{SECTIONS/ANDRE/2-4}


%--------------------BALANCING--------------------%

\input{SECTIONS/RENATO/3-1}

\input{SECTIONS/RENATO/3-2}


%--------------------EXAMPLE---------------------%

\input{SECTIONS/RENATO/4-1}

\input{SECTIONS/RENATO/4-2}

\input{SECTIONS/RENATO/4-3}

\input{SECTIONS/ANDRE/4-4}


%--------------------CONCLUSIONS--------------------%

%\newpage

\input{SECTIONS/TARCISIO/5}


%--------------------ACKNOWLEDGMENTS--------------------%

\section*{Acknowledgments}


%--------------------BIBLIOGRAPHY--------------------%

% \newpage
\phantomsection 
\input{EXTRAS/bibliography}


% \end{multicols}


\end{document}

