\begin{thebibliography}{10}

\bibitem{Rynaldo}
Rynaldo Z. H. de Almeida.
\newblock Modelagem din\~amica e controle e rob\^o manipulador
de arquitetura paralela assim\'etrica de tr\^es graus de liberdade.
\newblock {\em Tese (Doutorado) - Escola Polit\'ecnica da Universidade de
S\~ao Paulo. Departamento de Engenharia Mecatr\^onica e de
Sistemas Mec\^anicos},
  2013.
  
\bibitem{Andre}
Andr\'e G. Coutinho and Guilherme M. Dobriankyj.
\newblock Plataforma rob\'otica para reabilita\c{c}\~ao do membro superior humano.
\newblock {\em Tese (Trabalho de Conclus\~ao de Curso) - Escola Polit\'ecnica da Universidade de
S\~ao Paulo. Departamento de Engenharia Mecatr\^onica e de
Sistemas Mec\^anicos}, 2013.

\bibitem{Andre2}
Guilherme M. Dobriankyj, Andr\'e G. Coutinho and Tarcisio A. Hess Coelho.
\newblock Development of a controllerfor a 3-DOF robotic platform for user interaction in rehabilitation therapies.
\newblock {\em Biomedical Robotics and Biomechatronics (2014 5th IEEE RAS \& EMBS International Conference on},
  1(1):819 -- 824, 2014.


\bibitem{Apostila}
Renato M. M. Orsino and Tarcisio A. Hess Coelho.
\newblock Metodologia para An\'alise e S\'intese de Mecanismos.
\newblock {\em Material de apoio para as disciplinas PMR2430 e PMR2331 - Escola Polit\'ecnica da Universidade de
S\~ao Paulo}, 2013.

\bibitem{Craig}
J.J. Craig.
\newblock {\em {Introduction to robotics: mechanics and control}}.
\newblock Addison-Wesley series in electrical and computer engineering: control
  engineering. Pearson/Prentice Hall, 2005.
  
\bibitem{Jarzebowska2009}
Elzbieta Jarzebowska.
\newblock Quasi-coordinates based dynamics modeling and control design for
  nonholonomic systems.
\newblock {\em Nonlinear Analysis: Theory, Methods and Applications},
  71(12):e118 -- e131, 2009.

\bibitem{Merlet2002}
J.P. Merlet.
\newblock {Still a long way to go on the road for parallel mechanisms}.
\newblock In {\em ASME DETC Conference, {Montreal, 2002}}, 2002.

\bibitem{Orsino2013}
Renato M.~M. Orsino and Tarcisio A.~Hess Coelho.
\newblock A contribution for developing more efficient dynamic modelling
  algorithms of parallel robots.
\newblock {\em International Journal of Mechanisms and Robotic Systems},
  1(1):15 -- 34, 2013.

\bibitem{Zubizarreta}
Zubizarreta, A. and Cabanes, I. and Marcos, M. and Pinto, C. and Portillo, E.
\newblock Extended CTC control for parallel robots.
\newblock {\em Emerging Technologies and Factory Automation (ETFA), 2010 IEEE Conference on}, 2010.

\bibitem{Bloch}
Bloch, A.M. and Reyhanoglu, M. and McClamroch, N.H.
\newblock Control and stabilization of nonholonomic dynamic systems.
\newblock {\em Automatic Control, IEEE Transactions on}, 1992.

\bibitem{Slotini}
Slotine, Jean-Jacques E. and Li, Weiping.
\newblock {\em {Applied nonlinear control}}.
\newblock Prentice Hall, 1991.


\end{thebibliography}
