

\begin{thebibliography}{99}


\bibitem{1wijk} 
V. Van der Wijk,
\newblock Shaking moment balancing of mechanisms with principal vectors and moments
\newblock {\em Front. Mech. Eng.}, 8(1): 10--16, 2013.
 
\bibitem{2arakelian}
V. H. Arakelian V. , M. R. Smith,
\newblock Design of planar 3-dof 3-RRR reactionless parallel manipulators
\newblock {\em Mechatronics}, 18: 601--606, 2008. 
 
\bibitem{3seo}
J.-T. Seo, J. H. Woo, H. Lim, J. Chung, W. K. Kim, and B.-J. Yi,
\newblock Design of an Antagonistically Counter-Balancing Parallel Mechanism
\newblock {\em IEEE/RSJ International Conference on
Intelligent Robots and Systems (IROS)}, Tokyo, November 3-7: 2882--2887, 2013. 

\bibitem{4wu}
Y. Wu, C. M. Gosselin,
\newblock Design of reactionless 3-dof and 6-dof parallel manipulators using parallelepiped mechanisms
\newblock {\em IEEE Transactions on Robotics}, 21(5): 821--833, 2005.

\bibitem{5gosselin}
C. M. Gosselin, F. Vollmer, G. Côté, Y. Wu,
\newblock Synthesis and design of reactionless three-degree-of-freedom parallel mechanisms
\newblock {\em IEEE Transactions on Robotics and Automation}, 20(2): 191--199, 2004.

\bibitem{6wang}
J. Wang, C. M. Gosselin,
\newblock Static balancing of spatial four-degree-of-freedom parallel mechanisms
\newblock {\em Mech. Mach. Theory}, 35: 563--592, 2000.

\bibitem{7wang}
J. Wang, C. M. Gosselin,
\newblock Static balancing of spatial three-degree-of-freedom parallel mechanisms
\newblock {\em Mech. Mach. Theory}, 34: 437--452, 1999.

\bibitem{8alici}
G. Alici, B. Shirinzadeh,
\newblock Optimum Force Balancing with Mass Distribution and a Single Elastic Element for a
Five-bar Parallel Manipulator
\newblock {\em Proceedings of the IEEE International Conference on Robotics and Automation},Taipei, September 14-19: 3666--3671, 2003.

\bibitem{9alici}
G. Alici, B. Shirinzadeh,
\newblock Optimum dynamic balancing of planar parallel
manipulators based on sensitivity analysis
\newblock {\em Mech. Mach. Theory}, 41: 1520--1532, 2006.

\bibitem{10dehkordi}
M. B. Dehkordi, A. Frisoli, E. Sotgiu, M. Bergamasco,
\newblock Modelling and Experimental Evaluation of a Static Balancing Technique for
a new Horizontally Mounted 3-UPU Parallel Mechanism
\newblock {\em International Journal of Advanced Robotic Systems}, 9: 193--205, 2012.

\bibitem{11wang}
K. Wang, M. Luo, T. Mei, J. Zhao, Y. Cao,
\newblock Dynamics Analysis of a Three-DOF Planar Serial-Parallel Mechanism for Active
Dynamic Balancing with Respect to a Given Trajectory
\newblock {\em International Journal of Advanced Robotic Systems}, 10: 23--33, 2013.

\bibitem{12russo}
A. Russo, R. Sinatra, F. Xi,
\newblock Static balancing of parallel robots
\newblock {\em Mech. Mach. Theory}, 40: 191--202, 2005.

\bibitem{13agrawal}
S. K. Agrawal, A. Fattah,
\newblock Gravity-balancing of spatial robotic manipulators
\newblock {\em Mech. Mach. Theory}, 39: 1331--1344, 2004.

\bibitem{14briot}
S. Briot, V. Arakelian, J.-P. Le Baron,
\newblock Shaking force minimization of high-speed robots via centre of mass
acceleration control
\newblock {\em Mech. Mach. Theory}, 57: 1--12, 2012.

\bibitem{15coelho}
T. A. H. Coelho, L. Yong, V. F. A. Alves,
\newblock Decoupling of dynamic equations by means of
adaptive balancing of 2-dof open-loop mechanisms
\newblock {\em Mech. Mach. Theory}, 39: 871--881, 2004.

\bibitem{16moradi}
M. Moradi, A. Nikoobin, S. Azadi,
\newblock Adaptive Decoupling for Open Chain Planar Robots
\newblock {\em Transaction B: Mechanical Engineering}, 17(5): 376--386, 2010.

\bibitem{17arakelian}
V. Arakelian, S. Sargsyan,
\newblock On the design of serial manipulators with decoupled dynamics
\newblock {\em Mechatronics}, 22: 904--909, 2012.

\bibitem{18tsai}
J. Chen, D.Z. Chen, L.W. Tsai,
\newblock A Systematic Methodology for the Dynamic Analysis of Articulated Gear-Mechanisms,
\newblock 1990.

\bibitem{19kane}
T. R. Kane, D. A Levinson,
\newblock {\em {Dynamics, Theory and Applications}}.
\newblock McGraw-Hill series in mechanical engineering. McGraw Hill, 1985.

\bibitem{20orsino}
R. M. M. Orsino, A. G. Coutinho, T. A. H. Coelho (2014).
\newblock Dynamic modelling and control of balanced parallel mechanisms.
\newblock Manuscript submitted for publication

\bibitem{21orsino}
R. M. M. Orsino, T. A. H. Coelho (2015).
\newblock A contribution on the modular modelling of multibody systems.
\newblock Manuscript submitted for publication

\end{thebibliography}


\end{document}